Make any stupid plot you want

### 2020-12-29 draft/sections/math.tex
trying to pin action versus versus group

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|C|L|}\hline
     $\nu_{i}$                      & $\mu_{i}$                                                            & $dom(\nu_{i})$  \\ \hline                                              
    position                    & x, y, z                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}$   \\ \hline
    shape                       & markerstyle                                                      & $((\mathbb{R}, \mathbb{R}), x \in \{0,1,2,3,4,79\})^{n}^{\dag}$ \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $/^*\backslash^*-^*+^*x^*o^*O^*.^**^* \in \Sigma^{+}$ \newline $\Sigma=\{/, \backslash, |, -, +, x, o, O, ., *\}^{\ddag}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{Z}, (\mathbb{Z}^n))^{\dag}$ \\ \hline              
    \end{tabulary}
    \caption{\\
        \footnotesize{\dag $n>0$}\\
        \footnotesize{\ddag$\Sigma^+=\cup_{n\in\mathbb{Z}^+}\Sigma^n$}

    }
\end{table}

\subsubsection{Visual Channels}
The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_1 \arrow[r] \arrow[r, "\nu"] \arrow[d, "f"'] & V_1 \arrow[d, "f"] \\
    E_2 \arrow[r, "\nu"]                           & V_2               
\end{tikzcd}
\end{equation}

@@

@@

%%throw out this diagram
%%something about pushforward ...
%% \mu is pushfowwards of \tau = \mu = \nu(lowercase * ,\tau), \nu: *\tau \mapsto \mu
%% \nu acts from subspace E to subspace V
The constraint on $\nu: \tau\rightarrow \mu$

%%set up proofs here, are x&y transfereble here? (x,y coupled together, Es bundled by what nu is promosing, maps over to V in indepdent ways 
%E ^ V decomposed in one to one correspondances, \nu_0 is map from E_0 to V_0...\nu_n from E_n, V_n...., \nu = {\nu_0....\nu_n}

\paragraph{Allowable Maps}
For example, stevens: preserve structure ....
Some examples of allowable maps are described in Bertin/Munzner:
nus are constrained to preserve..., expect functorial nus - transform on input side to transform on output side (E1-E1, V1-V1, nu) <- condition
that's how we're constraining nu. 
functorial in $\nu$ component

>>>>

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \label{tab:mpl_visual_variable_fiber}
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{N}, \mathbb{N}^{n})$ \\ \hline              
    \end{tabulary}
\end{table}

\subsubsection{Visual Channels}

A monoid is a set with a closed operation

The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}

@@

The Stevens measurement scales\cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale} are examples of some of the group actions th

@@
